Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
fin mov p

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:socres) D). Graph strength did not change in
forest layers with increasing spatial resolution (Figure \@ref(fig:socres) E).
Foraging and open layer had greater individual variation in graph strength, and
foraging layers showed an increase in graph strength with increasing spatial
resolution (Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the
landscape) on Fogo Island and the proportion of relocations in foraging habitat
decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m).
Despite this, at 30 m resolution the foraging layer had similar edge overlap as
the open layer indicating its importance in caribou sociality. As such,
multilayer network measures related to habitat are explicitly dependent on
spatial scale.  If the spatial resolution of the habitat data are insufficient
to capture rare habitats, for example, context-specific relationships between
individuals may not be captured.

<!-- habitat+social -->

@@

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments.<!--  <- long sentence with two coulds --> For example, social processes may be an 
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

<!-- 
TODO: cut down to this

Given recent technological advancements in biologging and wildlife tracking technology 
[@Borger_2020], remotely sensed data provides a unique opportunity to use
multilayer social network analysis to answer complex questions about animal
socioecology

track the fine-scale movements of groups over large distances and time scales
[@Torney_2018]
-->

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
advanced to the point where relocations can be programmed to occur as frequently
as each second [@B_rger_2016], a practice which has been applied to questions of
collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
technology, including unmanned aerial vehicles and satellites, can be used to
track the fine-scale movements of groups over large distances and time scales
[@Torney_2018]. Using technology to infer behaviour has therefore become
standard operating procedure for many species in many systems. Our ability to
collect and process remotely sensed data and infer social processes based on
animal movement provides an opportunity to use multilayer social network
analysis to answer complex questions about animal socioecology.

>>>>

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat type as in
Figure \@ref(fig:lcres). Since habitat data are available across a range of
spatial scales, we evaluated the influence of increasing spatial resolution on
multilayer network metrics. As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:socres) D). Graph strength did not change in
forest layers with increasing spatial resolution (Figure \@ref(fig:socres) E).
Foraging and open layer had greater individual variation in graph strength, and
foraging layers showed an increase in graph strength with increasing spatial
resolution (Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the
landscape) on Fogo Island and the proportion of relocations in foraging habitat
decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m).
Despite this, at 30 m resolution the foraging layer had similar edge overlap as
the open layer indicating its importance in caribou sociality. As such,
multilayer network measures related to habitat are explicitly dependent on
spatial scale.  If the spatial resolution of the habitat data are insufficient
to capture rare habitats, for example, context-specific relationships between
individuals may not be captured.
<!-- habitat+social -->

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology [@Border_2020] have provided a
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

@@
